Planar Maximal Covering with Ellipses

### 2019-05-05 quali/quali.presentation/figures/fig:array_disks.tex
WIP

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95

@@

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

% Text Node
\draw (20,35) node [scale=0.5]  {$E_{1}$};
\end{tikzpicture}

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1.4,xscale=1.4]
%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95

@@

\draw (60,73) node [scale=0.6]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6]  {$4_-$};

% Text Node
\draw (20,35) node [scale=0.5]  {$D_{1}$};
\end{tikzpicture}

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_1.tex
WIP

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5,color=red]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\draw (60,73) node [scale=0.6]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6,color=red]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6]  {$4_-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_2.tex
WIP

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\draw (60,73) node [scale=0.6]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6,color=red]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6]  {$4_-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_2_5.tex
WIP

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5,color=red]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\draw (60,73) node [scale=0.6, color=red]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6]  {$4_-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_3.tex
WIP

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5,color=red]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\draw (60,73) node [scale=0.6]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6,color=red]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6]  {$4_-$};

@@

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, color=red,minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_4.tex
WIP

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_5.tex
WIP

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
	$+$ & $-$ & $-$ & $-$ & $+$ & $+$ & $+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

>>>>

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_6.tex
WIP

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5,color=red]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5]  {$-$};

% Text Node
\draw (20,35) node [scale=0.5]  {$D_{1}$};
\end{tikzpicture}
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,95); %set diagram left start at 0, and has height of 95

%Shape: Circle [id:dp8913971633985722] 
\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 } ,draw opacity=1 ] (33,53.5) .. controls (33,39.69) and (44.19,28.5) .. (58,28.5) .. controls (71.81,28.5) and (83,39.69) .. (83,53.5) .. controls (83,67.31) and (71.81,78.5) .. (58,78.5) .. controls (44.19,78.5) and (33,67.31) .. (33,53.5) -- cycle ;

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5,color=red]  {\textbf{$-$}};

@@

>>>>

\draw (60,73) node [scale=0.6]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6,color=red]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6]  {$4_-$};

@@

\begin{tikzpicture}

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

\node at (-4,-0.5) {$0$};
\node at (0,-0.5) {$2\pi$};
\end{tikzpicture}

### 2019-05-05 quali/quali.presentation/figures/mcd_sim_7.tex
WIP

\draw (60,73) node [scale=0.5]  {$+$};
% Text Node
\draw (65.22,66) node [scale=0.5]  {$+$};
% Text Node
\draw (74.22,50) node [scale=0.5]  {$+$};
% Text Node
\draw (54.22,39.56) node [scale=0.5]  {$-$};
% Text Node
\draw (45.62,36.96) node [scale=0.5]  {$-$};
% Text Node
\draw (38.02,31.56) node [scale=0.5,color=red]  {\textbf{$-$}};

@@

>>>>

\draw (60,73) node [scale=0.6]  {$4_+$};
% Text Node
\draw (65.22,66) node [scale=0.6]  {$3_+$};
% Text Node
\draw (74.22,50) node [scale=0.6]  {$2_+$};
% Text Node
\draw (64.22,36.56) node [scale=0.6]  {$2_-$};
% Text Node
\draw (54.32,40.66) node [scale=0.6]  {$3_-$};
% Text Node
\draw (44.02,39.56) node [scale=0.6,color=red]  {$4_-$};

@@

\begin{tikzpicture}

\matrix [matrix of nodes,row sep=,row sep=0mm,
column 1/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 2/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 3/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 4/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 5/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 6/.style={nodes={rectangle,draw,minimum width=1.5em, minimum height=0.5em}},
column 7/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 8/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 9/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 10/.style={nodes={rectangle,draw,minimum width=1.5em, color=red, minimum height=0.5em}},
column 11/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}},
column 12/.style={nodes={rectangle,draw,minimum width=1.5em, color=gray, minimum height=0.5em}}
] (O)
{
$2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$ & $2_+$ & $2_-$ & $3_-$ & $4_-$ & $4_+$ & $3_+$\\
	%$+$ & $-$ & $-$ & $-$ & $+$ & $+$\\
};

\node at (-4,-0.5) {$0$};
\node at (0,-0.5) {$2\pi$};
\end{tikzpicture}
